On the combination of Set Functions and Failures

### 2014-12-04 docs/src/overview.tex
Added documentation for configurable profiling option

Installation instructions for \CYS can be found in
the file \code{INSTALL.txt} stored in the \CYS installation directory.
Note that there are two possibilities to install \CYS:
\begin{description}
\item[Global installation:]\index{global installation}\index{installation!global}
\CYS is installed in some global system directory where users
have no write permission. In this case, some options for experimenting
with \CYS (like \code{supply} or \code{ghc}, see below)
are not available (since they require the recompilation of parts of
the installed system).
\item[Local installation:]\index{local installation}\index{installation!local}
\CYS is installed in some local user directory where the user
has write permission and the option \code{GLOBALINSTALL}
in the \code{Makefile} of the \CYS installation is set as follows:
\begin{lstlisting}
GLOBALINSTALL=no
\end{lstlisting}
In this case, all options of \CYS are available.
\end{description}
In the following, \cyshome denotes the installation directory
of the \CYS installation.

>>>>

Installation instructions for \CYS can be found in
the file \code{INSTALL.txt} stored in the \CYS installation directory.
Note that there are two possibilities to install \CYS:
\begin{description}
\item[Global installation:]\index{global installation}\index{installation!global}
\CYS is installed in some global system directory where users
have no write permission. In this case, some options for experimenting
with \CYS (like \code{supply} or \code{ghc}, see below)
are not available (since they require the recompilation of parts of
the installed system).
\item[Local installation:]\index{local installation}\index{installation!local}
\CYS is installed in some local user directory where the user
has write permission and the option \code{GLOBALINSTALL}
in the \code{Makefile} of the \CYS installation is set as follows:
\begin{lstlisting}
GLOBALINSTALL=no
\end{lstlisting}
In this case, all options of \CYS are available.
\end{description}

Furthermore, \CYS can be installed with experimental support for profiling
of executables. To use profiling, two requirements have to be met:
\begin{itemize}
\item The libraries that are shipped with the GHC that is used by \CYS
have to be installed with profiling enabled. This is the default for the system
libraries contained in the GHC release, but may not be the case for additional
libraries.
\item The \code{Makefile} of \CYS contains an option \code{PROFILING}
which has to be set to \code{yes} to enable profiling support. You may
either change the Makefile to
\begin{lstlisting}
PROFILING = yes
\end{lstlisting}
or specify this setting while starting the installation process using
\begin{lstlisting}
make <optional target> PROFILING=yes
\end{lstlisting}

In the following, \cyshome denotes the installation directory
of the \CYS installation.
